Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec4-experiments.tex
change sec4

\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
%
We found that the performance of GNNs on all datasets was consistent with the training stage (\figurename~\ref{fig:exp_memory_expansion_ratio}). 
%

% added by wangyunpan, 2020-12-22 ----end----

>>>>

\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
%
We found that The performance of GNNs on all datasets was consistent with the training stage in \figurename~\ref{fig:exp_memory_expansion_ratio}, but the corresponding values were lower.
%

%
% added by wangyunpan, 2020-12-22 ----end----
